A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-02-19 paper/paper.tex
Stated line number of counting loop in comparison with CP section

CP-FC uses a soft all-different constraint to compute a bound, which requires
running a matching algorithm on a supporting compatibility graph.  Careful
thought shows that \McSplit\ computes the same bound, but using a simple
counting loop---this is only possible because of the disjoint nature of the
domains.

>>>>

CP-FC uses a soft all-different constraint to compute a bound, which requires
running a matching algorithm on a supporting compatibility graph.  Careful
thought shows that \McSplit\ computes the same bound, but using a simple
counting loop (\cref{McSplitAlg}, \lineref{CalcBound})---this is only possible
because of the disjoint nature of the domains.
